### 2016-06-28 sec6_experiment.tex
An almost complete version
Near Done

\subsection{Performance Evaluation}
\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping vary $G$}
    \end{subfigure}

	\begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
        \caption{Geolife vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
        \caption{Geolife vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
        \caption{Geolife vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
        \caption{Geolife vary $G$}
    \end{subfigure}

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}
\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.

\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(f),(j).  SPARE tends to run faster, whereas the performance of TRPM degrades dramatically. This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$. However, the line sweep algorithm in TRPM does not utilize such property for pruning. It takes longer time because more replication data has to be handled in each partition.

\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) present the performances with varying $L$. When $L=10$, SPARE can outperform TRPM by around $10$ times. We also observe that there is a significant performance improvement for TPRM when $L$ increases from $10$ to $20$ and later the running time drops smoothly. 
This is because $\eta$ is proportional to $O(K*G/L+L)$. When $L$ is small (i.e., from $10$ to $20$),
$\eta$ decreases drastically. As $L$ further grows, $\eta$ varies less significantly.

\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) present the performances with increasing $G$.  TRPM is rather sensitive to $G$. When $G$ is relaxed to larger values, more valid patterns would generate. TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$. In contrast, with much more effective pruning strategy, our SPARE scales very well with $G$.

\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary_OT} (a)(b)(c) present 
the performances with increasing number of moving objects. Both TRPM and SPARE take longer time to find patterns in a growing database. We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.

\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary_OT} (d)(e)(f) present 
the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.

\begin{figure}[h]
\centering
	\begin{subfigure}[b]{0.22\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
        \caption{Shopping vary $O_r$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
        \caption{Geolife vary $O_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
        \caption{Taxi vary $O_r$}
    \end{subfigure}
    \begin{subfigure}[b]{0.22\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
        \caption{Shopping vary $T_r$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
        \caption{Geolife vary $T_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
        \caption{Taxi vary $T_r$}
    \end{subfigure}
 \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
 \label{exp:performance_vary_OT}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & STD        & Straggler       & STD      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time among executors,units are in seconds.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load Balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most empty reducers.
Figure~\ref{exp:wl}(a) shows the break-down costs in the map-reduce stages for SPARE and SPARE-RD. We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE spends additional time cost to make an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). We also report the cost of straggler, i.e., the longest job, in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

@@

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{Geolife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE and Platoon}
 \label{exp:scalability}
\end{figure*}

>>>>

\subsection{Performance Evaluation}
\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping vary $G$}
    \end{subfigure}
	\begin{subfigure}[b]{0.16\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
        \caption{Shopping vary $O_r$}
    \end{subfigure}
        \begin{subfigure}[b]{0.16\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
        \caption{Shopping vary $T_r$}
    \end{subfigure}

	\begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
        \caption{Geolife vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
        \caption{Geolife vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
        \caption{Geolife vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
        \caption{Geolife vary $G$}
    \end{subfigure}       
 	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
        \caption{Geolife vary $O_r$}
    \end{subfigure}
 	\begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
        \caption{Geolife vary $T_r$}
    \end{subfigure}

    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}   
	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
        \caption{Taxi vary $O_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
        \caption{Taxi vary $T_r$}
    \end{subfigure}

\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}
\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(g),(m)
present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.

\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(h),(n).  SPARE tends to run faster, whereas the performance of TRPM degrades dramatically. This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$. However, the line sweep algorithm in TRPM does not utilize such property for pruning. It takes longer time because more replication data has to be handled in each partition.

\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c),(i),(o) present the performances with varying $L$. When $L=10$, SPARE can outperform TRPM by around $10$ times. We also observe that there is a significant performance improvement for TPRM when $L$ increases from $10$ to $20$ and later the running time drops smoothly. 
This is because $\eta$ is proportional to $O(K*G/L+L)$. When $L$ is small (i.e., from $10$ to $20$),
$\eta$ decreases drastically. As $L$ further grows, $\eta$ varies less significantly.

\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d),(j),(p) present the performances with increasing $G$.  TRPM is rather sensitive to $G$. When $G$ is relaxed to larger values, more valid patterns would generate. TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$. In contrast, with much more effective pruning strategy, our SPARE scales very well with $G$.

\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present 
the performances with increasing number of moving objects. Both TRPM and SPARE take longer time to find patterns in a growing database. We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.

\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary} (f),(l),(r) present 
the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.

%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

@@

\begin{table}[h]
\centering \small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time among executors,units are in seconds.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load Balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most empty reducers.
Figure~\ref{exp:wl}(a) shows the break-down costs in the map-reduce stages for SPARE and SPARE-RD. We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE spends additional time cost to make an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

@@

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{Geolife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE and Platoon}
 \label{exp:scalability}
\end{figure*}
